Weather Data Integration and Assimilation System\\

### 2020-02-10 Paper.tex
Fixed: sub section labels

\paragraph{Further improve hierarchical database performance}
As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute \ref{sub:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

@@

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \ref{sub:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

>>>>

\paragraph{Further improve hierarchical database performance}
As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

@@

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

### 2020-02-10 method/sec_4-db_struct.tex
Fixed: sub section labels

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Key Attributes}
\label{sub:timeseries_key_attributes}
\subsubsection{Module ID}
String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{rdbms}}
\label{sub:mysql}

There are lots of \acrshort{rdbms} available and for \acrshort{wdias} is using SQL as the \acrfull{rdbms}.
SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
\ref{db_struct_redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{sub:influxdb}
Among the other timeseries open source databases available, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} has higher number of usage and support. Database is written in Golang programming language, and has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another Database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrfull{netCDF}} 
\label{sub:netcdf}
\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
And it also has the support for parallel file access.
NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data.
Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Document-oriented Database}
\label{sub:mongodb}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{sub:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Key Attributes}
\label{subse:timeseries_key_attributes}
\subsubsection{Module ID}
String field which describe the source of the data generated. e.g., hec-hms, flow2d, weather-station etc

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{rdbms}}
\label{subse:mysql}

There are lots of \acrshort{rdbms} available and for \acrshort{wdias} is using SQL as the \acrfull{rdbms}.
SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
\ref{subse:redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among the other timeseries open source databases available, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} has higher number of usage and support. Database is written in Golang programming language, and has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another Database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrfull{netCDF}} 
\label{subse:netcdf}
\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
And it also has the support for parallel file access.
NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data.
Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Document-oriented Database}
\label{subse:mongodb}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}

### 2020-02-10 results/sec_2-workload.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.
Fixed: sub section labels

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.jpg}
    \caption{Experimental Setup with JMeter}
    \label{fi:experimental_setup}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
    \caption{WDIAS Performance Test - Throughput Shaping Timer Graph}
    \label{fi:test_prod_throughtput_shaping_timer}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{System Configuration}
\label{sub:test_sys_config}
As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, Digital Ocean etc on the cloud.

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.jpg}
    \caption{Experimental setup with JMeter}
    \label{fi:experimental_setup}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/test_prod_throughtput_shaping_timer.png}
    \caption{\acrshort{wdias} performance test - Throughput Shaping Timer graph}
    \label{fi:test_prod_throughtput_shaping_timer}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{System Configuration}
\label{subse:test_sys_config}
As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, Digital Ocean etc on the cloud.
